\chapter{Methodology}
\label{ch:methodology}

This literature review follows the PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses) guidelines to ensure a transparent and reproducible selection process \cite{keemink2018admittance}.

\section{Search Strategy}
To identify relevant literature on control strategies for mechanically coupled assistive devices, we conducted searches in the following electronic databases:
\begin{itemize}
    \item IEEE Xplore
    \item Scopus
    \item Google Scholar
    \item PubMed (for pHRI/ergonomics)
\end{itemize}

\subsection{Search Queries}
Two clusters of queries were designed to cover the primary (control) and secondary (inference) research directions:

\textbf{Cluster A: Anisotropic Admittance Control (Primary Focus)}
\begin{enumerate}
    \item \texttt{("admittance control" OR "impedance control") AND ("unknown environment" OR "unknown surface") AND ("pHRI")}
    \item \texttt{("anisotropic" OR "directional") AND ("admittance" OR "compliance") AND ("robot")}
    \item \texttt{("variable admittance") AND ("intent" OR "intention") AND ("physical human-robot interaction")}
\end{enumerate}

\textbf{Cluster B: Active Inference in pHRI (Secondary Focus)}
\begin{enumerate}
    \item \texttt{("active inference" OR "free energy principle") AND ("robot") AND ("interaction" OR "shared control")}
\end{enumerate}

\section{Selection Criteria}
Studies were screened based on the following criteria:

\subsection{Inclusion Criteria}
\begin{itemize}
    \item Peer-reviewed journal articles and major conference proceedings (IEEE ICRA, pedestrian HRI, pedestrian Robotics and Automation Letters).
    \item Published between 2015 and 2025 (to capture recent advancements while including foundational work).
    \item Focus on continuous contact tasks (e.g., surface following, grinding, polishing) OR force control in constrained environments.
    \item Involves physical coupling between human and robot (not pure teleoperation without haptic feedback).
\end{itemize}

\subsection{Exclusion Criteria}
\begin{itemize}
    \item Studies focused solely on free-motion gestures (no contact with environment).
    \item Fully autonomous systems with no human-in-the-loop.
    \item Medical/Rehabilitation exoskeletons (unless control logic is directly transferable to industrial tool assistance).
    \item Pure simulation studies without hardware validation (unless foundational/theoretical).
\end{itemize}

\section{Data Extraction}
For each included study, the following information was extracted:
\begin{itemize}
    \item Control architecture (admittance, impedance, hybrid).
    \item Assumptions about environment geometry (known/unknown surface).
    \item Human intent estimation method (if any).
    \item Experimental validation (simulation, hardware, user study).
    \item Key findings and limitations.
\end{itemize}
